---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(lubridate)
library(forcats)
library(hms)
library(haven)

```

```{r}
getwd()

```


## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Data Preparation

Loading required data:

```{r cars}
#Loading survey data
sur <- readRDS("survey/meof_usa_survey_df.RDS")
#Loading data of web tracking
web <- readRDS("tracking/meof_usa_web_df.RDS")
#Loading timezones data
tf <- readRDS("tracking/time_zones.RDS")

#We need to take data on digit code of states
url <- "https://www2.census.gov/geo/docs/reference/state.txt"
download.file(url, destfile = "state.txt", mode = "wb")

# Read the text file into a dataframe
state_df <- read.table("state.txt", header = TRUE, sep = "|")

```

Creating dataframe containing only the Netflix content consumption

```{r}
# # Step 1: Filtering and merging Netflix data
# net_st <- web %>% 
#   filter(grepl("netflix", domain, ignore.case = TRUE)) %>%
#   semi_join(sur %>% select(personid, inputstate) %>% filter(!is.na(inputstate)) %>% distinct(), by = "personid")
# 
# #Preparing data of state_df for merging:
# state_df <- state_df %>% 
#   rename(
#     inputstate = STATE,
#     state = STATE_NAME
#   )
# 
# # Step 2: Merging state_df data
# net_st <- net_st %>% 
#   left_join(state_df %>% select(inputstate, state), by = "inputstate")
# 
# # Step 3: Adding timezone variable
# net_st <- net_st %>% 
#   left_join(tf, by = "state")
```


```{r}
#filtering the domain variable only by Netflix:
netflix <- web %>% 
  filter(grepl("netflix", domain, ignore.case = TRUE))
#merging netflix data adding data on state of residence of users
net_st <- merge(netflix, sur[, c("personid", "inputstate")], by = "personid", all.x = FALSE)
#removing NAs and duplicated data
net_st <- net_st %>%
  filter(!is.na(inputstate)) %>%
  distinct()

#Preparing data of state_df for merging:

state_df <- state_df %>% 
  rename(
    inputstate = STATE,
    state = STATE_NAME
  )
#Firstly, we merge net_sf dataframe to add names of states in addition to digit codes
net_st2 <- merge(net_st, state_df[, c("state", "inputstate")], by = "inputstate", all.x = FALSE)
#Then, we add timezone variable from tz dataframe
net_st3 <- merge(net_st2, tf, by = "state")


```

Now we have the dataframe with appropriate timezone, but we need to convert timestamps and extract weekdays for plotting 

```{r}
#Using lubridate library to change type of data in timestamp(used_at) variable
net_st3$used_at <- ymd_hms(net_st3$used_at, tz = "UTC")
#Converting timestamps according time zones and creating variable timestamps
net_st3$timestamps <- with_tz(net_st3$used_at, tzone = net_st3$time_zone)

#Using the Lubridate creating weekdays variable
net_st3$weekdays <- wday(net_st3$timestamps)

#Extracting data on the level of hour-minute-second

net_st3$hms <- as_hms(net_st3$timestamps)

```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
